\chapter{Data Collection and Understanding}

data collection and understanding play a pivotal role in extracting meaningful insights and deriving accurate conclusions.
The success of any analytical endeavor heavily relies on the quality, comprehensiveness, and relevance of the data used.
In the case of carbon emissions in maritime shipping, gathering and understanding the data is crucial for capturing the intricacies of this complex domain.
By exploring various data sources from industry databases, a comprehensive dataset can be acquired, encompassing diverse dimensions of carbon emissions in the maritime sector.
Furthermore, understanding the structure, variables, and limitations of the collected data is essential for ensuring the validity and reliability of subsequent analyses.
This includes examining the completeness of data, identifying any biases or data gaps, and verifying the accuracy of measurements.
Ultimately, a thorough and informed understanding of the data sets the foundation for conducting rigorous data analysis and generating actionable insights for addressing carbon emission challenges in maritime shipping.

Collaboration with Astrup Fearnleys Code has been instrumental in enhancing my research on carbon emissions in maritime shipping.
As a leading firm in the maritime shipping industry, their expertise and industry connections have provided me with invaluable support and access to crucial datasets.
Specifically, through their collaboration, I was able to gain access to two significant datasets: Automatic Identification System (AIS) data and IHS dataset.
Collaborating with Astrup Fearnleys Code and leveraging their industry expertise has not only provided me with valuable datasets but also allowed me to gain insights into the complex dynamics of the maritime shipping industry.

\newpage

\input{pages/chapters/dataCollection/ihs.tex}

\newpage


\input{pages/chapters/dataCollection/ais.tex}
