\chapter{Introduction}
\setcounter{page}{1}

\section{Background and Motivation}

In the 21st century, Climate change is the biggest challenge faced by humanity. It poses a substantial danger to the survival of the inhabitants of our planet.
Human activities such as deforestation and burning of fossil fuels have led to a rise in global temperatures.
Becuase of this rise, there has been a rise in sea levels, extreme weather events, and loss of biodiversity.
There is an urgent need to reduce greenhouse gas emissions and transition to a sustainable, low-carbon future.

Maritime is essential to the global economy, transporting 90\% of the world's goods by volume.
It is also a major source of greenhouse gas emissions, with the International Maritime Organization (IMO)
estimating that maritime shipping accounts for 3\% of global carbon dioxide emissions.
While 3\% may seem small, it is important to note that this is a rapidly growing sector.
Without action, maritime shipping contribution to carbon emissions can increase upto 10-13\% in the next few decades..
Due to this fact, there is a growing global effort to reduce emissions from this sector. \autocite{king_anthony_2022}.

In accordance with sustainable Development Goal 13, in 2018, the inital stratergy was adopted by IMO's Environmental Protection Committee (MEPC),
during its 72nd session at IMO Headquarters in London, United Kingdom. Accorging to this stratergy,
the IMO will work towards reducing the total annual greenhouse gas emissions from international shipping by at least 50\% by 2050 compared to 2008 \autocite{imo-2018}.
In 76th ssssion MEPC in 2021, serval mandatory measures were adopted to reduce greenhouse gas emissions from international shipping,
which will help in achieving the goal of reducing emissions by 50\% by 2050 \autocite{imo-2021}. One of the important measures is the carbon intensity indicator (CII).

Maritime shipping is a complex and highly volatile system, generating very large data sets.
Big data analytics can be used to understand the complex system and make informed decisions.
It can facilitate operations such as monitoring of emission and predictive analysis of vessel performance.
This can help in reducing emissions and improving the efficiency of the maritime sector \autocite{ZAMAN2017537}.


\input{pages/chapters/introduction/bigDataAnalysis.tex}
\input{pages/chapters/introduction/problemStatement.tex}
\input{pages/chapters/introduction/researchQuestion.tex}
\input{pages/chapters/introduction/outline.tex}